Bricking up backdoors in Intrusion Detection Systems

### 2019-09-11 ex2/paper/paper.tex
Change figure a little bit

\subsubsection{Identifying Backdoors}
\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/pdpale2017nn_joint.pdf}
%\includegraphics[width=\columnwidth]{figures/pdpale2017nn.pdf}

@@

It has to be noted, however, that inconsistent behaviour of the \gls{mui}, detected using \gls{pdp} or \gls{ale} plots, does not necessarily result from poisoning activity.  For example, \autoref{fig:ttlmean} shows the mean(TTL) feature in forward direction. The models show a clear dependence of the mean \gls{ttl} value of incoming packets, which is similarly counter-intuitive as for the feature discussed above. In our case, this behaviour results from the non-equal distribution of \gls{ttl} values of attack and non-attack traffic in both the \unsw{} and CIC-IDS-2017 datasets.

@@

\subsection{Pruning Techniques}
To perform pruning, a validation dataset is needed. We take a validation dataset that is one fourth the size of the training dataset. We use the validation dataset for pruning as described in the next sections and use a test dataset that is also one fourth to verify whether the backdoor can successfully be removed and how much the accuracy on the original data suffers. Training, validation and test dataset are pairwise disjoint.

@@

To ensure that no backdoor is contained in the model in question, it has to be carefully analyzed for questionable decisions. For this purpose, \gls{pdp} and \gls{ale} plots are an effective tool. In fact, already throughout the process of training of the model explainability plots constitute a useful tool to ensure that the model is not unintentionally trained  to artifacts the dataset yields.

@@

Another important takeaway is that the features used when deploying an \gls{ids} have to be selected carefully. Indeed, the implementation of a backdoor as conducted in this research is only possible when using several features involving the \gls{ttl} value. Even though it might seem tempting to provide all possible features to a \gls{dl} or \gls{rf} classifier and let it learn the most important ones, this strategy should be avoided.

>>>>

\subsubsection{Identifying Backdoors}
\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/pdpale2017nn_joint_2.pdf}
%\includegraphics[width=\columnwidth]{figures/pdpale2017nn.pdf}

@@

However, inconsistent behaviour of the \gls{mui}, detected using \gls{pdp} or \gls{ale} plots, does not necessarily result from poisoning activity.  For example, \autoref{fig:ttlmean} shows the mean(TTL) feature in forward direction. The models show a clear dependence of the mean \gls{ttl} value of incoming packets, which is similarly counter-intuitive as for the feature discussed above. In our case, this behaviour results from the non-equal distribution of \gls{ttl} values of attack and non-attack traffic in both the \unsw{} and CIC-IDS-2017 datasets.

@@

\subsection{Pruning Techniques}
To perform pruning, a validation dataset is needed. We take a validation dataset that is $\frac{1}{4}$ of the training dataset. We use the validation dataset for pruning as described in the next sections and use a test dataset that is also $\frac{1}{4}$ to verify whether the backdoor can successfully be removed and how much the accuracy on the original data suffers. Training, validation and test dataset are pairwise disjoint.

@@

To ensure that no backdoor is contained in the model in question, it has to be carefully analyzed for questionable decisions and potentially unnecessary features. For this purpose, \gls{pdp} and \gls{ale} plots are an effective tool. In fact, already throughout training process explainability plots constitute a useful tool to ensure that the model is not unintentionally trained  to artifacts the dataset yields. Indeed, the implementation of a backdoor as conducted in this research is only possible when using several features involving the \gls{ttl} value. Even though it might seem tempting to provide all possible features to a \gls{dl} or \gls{rf} classifier and let it learn the most important ones, this strategy should be avoided.

@@
